The \dealii Library, Version 9.2

### 2020-05-25 9.2/paper.tex
Leave a note.

By replacing the collective communications during set up and removing the arrays
that contain information for each process (enabled by the application of consensus
algorithms and other modifications---a full list of modifications leading to this
improvement can be found online), we were able to significantly
improve the set up
time for large-scale simulations and to solve a Poisson problem with multigrid
with \num{12e12} unknowns.
\todo[inline]{Where did we solve for 12T unknowns? The largest I [Martin] have done is 2.1T unknowns.}
Figure~\ref{} compares the timings of a simulation (including set up) with the
previous release 9.1 and with the current release 9.2.
{\color{red}TODO[Peter/Martin] description of the results}

>>>>

By replacing the collective communications during set up and removing the arrays
that contain information for each process (enabled by the application of consensus
algorithms and other modifications---a full list of modifications leading to this
improvement can be found online), we were able to significantly
improve the set up
time for large-scale simulations and to solve a Poisson problem with multigrid
with \num{12e12} unknowns.
\todo[inline]{Where did we solve for 12T unknowns? The largest I [Martin] have done is 2.1T unknowns.}
Figure~\ref{...} {\color{red}Update reference} compares the timings of a simulation (including set up) with the
previous release 9.1 and with the current release 9.2.
{\color{red}TODO[Peter/Martin] description of the results}
